\documentclass{layout/tudelft-aiaa}

%% Additional packages and commands
\renewcommand{\deg}{\si{\degree}\xspace}
\usepackage[newfloat]{minted} % (recommended)
\usepackage{comment}
\usepackage{biblatex}
\addbibresource{article.bib}
% Set global Minted options
\setminted{linenos, autogobble, frame=lines, framesep=2mm}

%% Defining title, author and affiliation
\title{A preCICE-OpenFAST adapter \\ to couple OpenFAST to CFD simulation tools \\ \vspace{4pt} \normalsize{Technical Report}}
\author{Leonard Willeke}
\affil{Delft University of Technology}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Begin of document %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\AlwaysPagewidth{

\maketitle

%% Abstract

\begin{abstract}
    \noindent
    Flow dynamics in wind parks are important for many engineering problems, ranging from optimized control to load reduction. This work introduces a preCICE-OpenFAST adapter designed to seamlessly couple OpenFAST with the preCICE library. preCICE facilitates the black-box coupling of simulation programs, enabling multi-physics simulations. The adapter acts as a driver code for OpenFAST, steering the turbine simulation and utilizing preCICE for efficient data exchange with the flow simulation. In a proof of concept, the adapter is employed to couple OpenFAST with OpenFOAM, demonstrating its potential despite limited capabilities. The presented approach lays the foundation for more comprehensive wind park simulations by integrating OpenFAST in the preCICE ecosystem. This research contributes to advancing wind park modeling techniques, providing a framework for studying complex interactions within wind farms.
\end{abstract}
}

%% Nomenclature

\renewcommand{\nompreamble}{\emph{Use this section to provide a list of all symbols used in the report. Provide a concise description. For example:}} %

\printnomenclature[\nomequalsign]

\nomenclature{$A$}{amplitude of oscillation}
\nomenclature{$C_p$}{pressure coefficient}
\nomenclature{$C_x$}{force coefficient in the x direction}
\nomenclature{$C_y$}{force coefficient in the y direction}
\nomenclature{$c$}{chord}
\nomenclature{$dt$}{time step}
\nomenclature{$F_x$}{X component of the resultant pressure force acting on the vehicle}
\nomenclature{$F_y$}{Y component of the resultant pressure force acting on the vehicle}
\nomenclature{$f, g$}{generic functions}
\nomenclature{$h$}{height}
\nomenclature{$i$}{time index during navigation}

%% Main body

\input{introduction}

\input{literature-review}

\input{software}

\input{example-cases}

\input{challenges}

\input{conclusion}

\section*{Acknowledgments}

I am grateful to Prof. Axelle Viré who accepted me as a visiting researcher and made this work possible. Many thanks to her and Evert Wiegant for the discussions and hints during our meetings. Extended thanks to Benjamin Uekermann, who enabled my visit at TU Delft in the first place and provided feedback along the way. Lastly, I want to thank the wonderful crowd of PhD researchers in the wind energy department who made my time in Delft memorable.

%% Bibliography

\printbibliography

%% Appendix
\begin{comment}
\section*{Appendix}

Possible points to include in the Appendix
\begin{itemize}
\item Files from the OpenFOAM adapter with hints on how to modify them
\item Files from AspFAST with hints on how to reuse the code for our mapping
\end{itemize}
\end{comment}


\end{document}
